Local PCA Shows How the Effect of Population Structure Differs Along the Genome

### 2018-08-09 writeup/local_pca_paper.tex
add missingness plots

>>>>

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_Drosophila_missings_against_MDS1_win103}
    \end{center}
    \caption{
        The missingness ratio along genome and the correlation of MDS against missingness in Drosophila.
        \label{sfig:dpgp_missingness}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_Medicago_missing_against_MDS1_win104}
    \end{center}
    \caption{
        The missingness ratio along genome and the correlation of MDS against missingness in Medicago.
        \label{sfig:medicago_missingness}
    }
\end{figure}
